State of the Art in \\ {\ttlit Twitter Sentiment Analysis}

### 2015-01-24 paper/chapters/3_preprocessing.tex
edit tagger section of the paper

\subsection{Tagger}
Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefor
very useful for Natural Language Processing.
Tagging Tweets is very challenging, because of the twitter specific slang, emoticons and the lack of conventional orthography.
%TODO: Quelle: Part-of-Speech Tagging for Twitter: Annotation, Features, and Experiments
There is a variety of freely downloadable POS taggers
\footnote{http://www-nlp.stanford.edu/links/statnlp.html} e.g. Stanford POS tagger
\footnote{http://nlp.stanford.edu/software/tagger.shtml}
 but just a few are specialized on tagging twitter data like the TweetNLP tagger
\footnote{http://www.ark.cs.cmu.edu/TweetNLP/}. In comparison with the Stanford POS tagger the TweetNLP tagger
 reduces errors by 25\%.
 %TODO Quelle: http://iswc2012.semanticweb.org/sites/default/files/76490497.pdf

>>>>

\subsection{Tagger}
Part-of-Speech (POS) tagging is a simple form of syntactic analysis and therefor
very useful for Natural Language Processing. The performance of POS taggers degrade
on out-of-domain data and tagging tweets poses additional challenges, e.g. the twitter
specific slang, emoticons and the lack of conventianal orthography. \autocite{Gimpel2011}
There is already a wide range of freely downloadable POS taggers \footnote{http://www-nlp.stanford.edu/links/statnlp.html},
e.g. the Standford POS tagger \footnote{http://nlp.stanford.edu/software/tagger.shtml}.
Because of the peculiarities of the language used in tweets, just a few of them are
specialized on tagging twitter data, like the TweetNLP tagger \footnote{http://www.ark.cs.cmu.edu/TweetNLP/}.
In comparison with the Stanford POS tagger the TweetNLP tagger reduces errors by 25\%. \autocite{Saif2012}
